Multi-channel Kondo model URG

### 2021-11-23 notes/multi-channel-urg.tex
improved the analytical derivation for the bath chi, mostly matches with numerics now, funniiy only the K=2 case doesnt match
obtained asymptotic beahviours of bath chi

\documentclass{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
\usepackage[margin=0.2in]{geometry}
\numberwithin{equation}{section}
\allowdisplaybreaks
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ebgaramond}
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Derivation of URG equations for the multi-channel Kondo model}

@@

Defining \(\epsilon^h_m = \frac{1}{2}\left(Jm + h\right) \) and \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
\begin{equation}\begin{aligned}
	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} 
\end{aligned}\end{equation}
The eigenvalues are 
\begin{equation}\begin{aligned}
	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}
\end{aligned}\end{equation}
where \(\alpha = \epsilon^h_m + J/4\).
The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\). The partition function is
\begin{equation}\begin{aligned}
	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
\end{aligned}\end{equation}
where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\). This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\). For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\). \(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\). So, \(s_\text{tot} = 1/2\) appears twice. These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different. We need to count the number of instances of a particular subspace \(s_\text{tot}=M\). It turns out that this number is given by
\begin{equation}\begin{aligned}
	r^K_M = {}^{K-1}C_{K/2 - M}
\end{aligned}\end{equation}
which means the correct partition function is
\begin{equation}\begin{aligned}
	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
\end{aligned}\end{equation}

@@

Defining \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
\begin{equation}\begin{aligned}
	H_m = mh + \begin{pmatrix} Jm/2 & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & h - J(m+1)/2 \end{pmatrix} 
\end{aligned}\end{equation}
The eigenvalues are 
\begin{equation}\begin{aligned}
	\lambda_{m, \pm}^{M, h} = -J/4 + mh \pm \sqrt{J^2x^M_m/4 + J^2/16 - Jmh/2}
\end{aligned}\end{equation}
The eigenvalues of the terminal states are \(JM/2 \pm hm\). The partition function is
\begin{equation}\begin{aligned}
	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
\end{aligned}\end{equation}
where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\). This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\). For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\). \(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\). So, \(s_\text{tot} = 1/2\) appears twice. These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different. We need to count the number of instances of a particular subspace \(s_\text{tot}=M\). It turns out that this number is given by
\begin{equation}\begin{aligned}
	r^K_M = {}^{K-1}C_{K/2 - M}
\end{aligned}\end{equation}
which means the correct partition function is
\begin{equation}\begin{aligned}
	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
\end{aligned}\end{equation}
\appendix

>>>>

\documentclass{revtex4-2}
\usepackage{braket,amsmath,amssymb,graphicx,float,hyperref,paralist}
\usepackage[margin=0.2in,top=0.5in,bottom=0.5in]{geometry}
\numberwithin{equation}{section}
\allowdisplaybreaks
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ebgaramond}
\begin{document}
\title{Multi-channel Kondo model URG}
\author{Abhirup Mukherjee}
\date{\today}
\maketitle
\section{Derivation of URG equations for the multi-channel Kondo model}

@@

Defining \(\epsilon^h_m = \frac{1}{2}\left(Jm + h\right) \) and \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
\begin{equation}\begin{aligned}
	H_m = \begin{pmatrix} \epsilon^h_m & \frac{J}{2}\sqrt{x^M_m} \\ \frac{J}{2}\sqrt{x^M_m} & -\left( \epsilon^h_m + J/2 \right)   \end{pmatrix} 
\end{aligned}\end{equation}
The eigenvalues are 
\begin{equation}\begin{aligned}
	\label{eigenvalue}
	\lambda_{m, \pm}^{M, h} = \frac{1}{2}\left[-J/2 \pm \sqrt{J^2/4 + J^2 x_m^M + 4\epsilon^h_m\left(\epsilon^h_m + J/2\right) }\right] = -J/4 \pm \sqrt{J^2x^M_m/4 + \alpha^2}
\end{aligned}\end{equation}
where \(\alpha = \epsilon^h_m + J/4\).
The eigenvalues of the terminal states are \(\pm\epsilon^h_{\pm M}\). For \(h = 0\), the ground state subspace is \(K-\)fold degenerate and is formed by the negative solutions of eq.~\ref{eigenvalue}. This common \(K-\)fold degenerate eigenvalue is \(-J(M+1)/2\). The partition function is
\begin{equation}\begin{aligned}
	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta \epsilon^h_{M}} + e^{\beta \epsilon^h_{- M}}\right] \\
	&=\sum_{M=M_\text{min}}^{M_\text{max}}\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
\end{aligned}\end{equation}
where \(M_\text{max} = K/2\) for a \(K-\)channel Kondo model, and \(M_\text{min} = 0\)  if \(K\) is even, otherwise \(1/2\). This is yet not the complete partition function, because we have not accounted for the possibility that there multiple subspaces of \(M\). For example, the \(K=3\) case states can be obtained by adding the third spin-half onto the states \(S=0,1\). \(S=0\) gives \(s_\text{tot}=1/2\) and \(S=1\) gives \(s_\text{tot} = 1/2, 3/2\). So, \(s_\text{tot} = 1/2\) appears twice. These two subspaces are actually orthogonal, because the quantum numbers for the individual channels are different. We need to count the number of instances of a particular subspace \(s_\text{tot}=M\). It turns out that this number is given by
\begin{equation}\begin{aligned}
	r^K_M = {}^{K-1}C_{K/2 - M}
\end{aligned}\end{equation}
which means the correct partition function is
\begin{equation}\begin{aligned}
	Z(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\sqrt{J^2x^M_m/4 + \alpha^2} + 2e^{-\beta JM/2}\cosh \beta h/2\right]
\end{aligned}\end{equation}

@@

Defining \(x^M_m = M(M+1) - m(m+1)\), the \(2\times 2\) blocks can be written as
	H_m = \begin{pmatrix} m(J/2 + h) & J\sqrt{x^M_m}/2 \\ J\sqrt{x^M_m}/2 & (m+1)(h - J/2) \end{pmatrix} 
The eigenvalues are 
	\lambda_{m, \pm}^{M, h} &= -J/4 + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2x^M_m + \left[(2m+1)h - J/2\right]^2 - 4m(m+1)(h^2 - J^2/4)} \\
				&= -J/4 + (2m+1)h/2 \pm \frac{1}{2}\sqrt{J^2(M + 1/2)^2 + h^2 - (2m+1)Jh}	= -J/4 + (2m+1)h/2 \pm \phi^M_m
The eigenvalues of the terminal states are \(JM/2 \pm hM\). The partition function is
	Z(h) &= \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left(e^{-\beta \lambda_{m, +}^{M, h}} + e^{-\beta \lambda_{m, -}^{M, h}}\right) + e^{-\beta JM/2}\left(e^{\beta hM} + e^{-\beta hM}\right)\right] \\
	     &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(J/4 - (m+1/2)h\right)}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\cosh \beta Mh\right]
We will now take the derivatives.
	Z^\prime(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta \left(J/4 - (m+1/2)h\right)}\left(-\beta (m+1/2) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)+ 2\beta Me^{-\beta JM/2}\sinh \beta Mh\right]\\
	Z^{\prime\prime}(h) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2 e^{\beta \left(J/4 - (m+1/2)h\right)}\left(\beta^2 (m+1/2)^2 \cosh \beta\phi^M_m - 2\beta^2 (m+1/2)\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right.\right.\\
			    &\quad\quad\quad\quad\quad\quad\left.\left. + \beta\frac{\:\mathrm{d^2}\phi^M_m}{\:\mathrm{d}h^2}\sinh \beta\phi^M_m + \beta^2\left(\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)^2 \cosh \beta\phi^M_m\right) + 2\beta^2 M^2 e^{-\beta JM/2}\cosh \beta Mh\right]\\
In the limit of \(h \to 0\), we  have
	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\phi^M_m + 2e^{-\beta JM/2}\right]\\
	Z^\prime(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\left(-\beta (m+1/2) \cosh \beta\phi^M_m + \beta\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right)\right]\\
	Z^{\prime\prime}(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2 e^{\beta J/4}\left(\beta^2 (m+1/2)^2 \cosh \beta\phi^M_m - 2\beta^2 (m+1/2)\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\sinh \beta\phi^M_m\right.\right.\\
			    &\quad\quad\quad\quad\quad\quad\left.\left. + \beta\frac{\:\mathrm{d^2}\phi^M_m}{\:\mathrm{d}h^2}\sinh \beta\phi^M_m + \beta^2\left(\frac{\:\mathrm{d}\phi^M_m}{\:\mathrm{d}h}\right)^2 \cosh \beta\phi^M_m\right) + 2\beta^2 M^2 e^{-\beta JM/2}\right]\\
The \(\phi\) and the derivatives are actually at \(h\to 0\). We are interested in the low temperature behaviour. In the limit of \(h \to 0\), \(\phi_m^M \to \phi^M = J(M+1/2)/2\). We can also look at the behaviour of the derivative:
	\lim_{h \to 0}\frac{\:\mathrm{d}\phi_m^M}{\:\mathrm{d}h} &= -\frac{J(m+1/2)}{4\phi^M}\\
	\lim_{h \to 0}\frac{\:\mathrm{d}^2\phi_m^M}{\:\mathrm{d}h^2} &= \frac{1}{4\phi^M} - \frac{J^2(m + 1/2)^2}{16\left(\phi^M\right)^3}\\
Substituting these gives
	     Z(h \to 0) &=\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}2e^{\beta J/4}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right] = \sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[4Me^{\beta J/4}\cosh \beta\phi^M + 2e^{-\beta JM/2}\right]\\
	Z^\prime(h \to 0) &=-\beta\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M2e^{\beta J/4} \left(\cosh \beta\phi^M + \frac{J}{4\phi^M}\sinh \beta\phi^M\right)\sum_{m=-M, \atop{m\in \mathbb{Z}}}^{M-1}\left( m + 1/2 \right) = 0\\
Z^{\prime\prime}(h \to 0) &=\beta^2\sum_{M=M_\text{min}}^{M_\text{max}}r^K_M\left[2 e^{\beta J/4}\left\{\left(1 + \frac{J^2}{16{\phi^M}^2}\right) \Sigma_M \cosh \beta\phi^M + \left(\frac{2M}{4\beta\phi^M} + \frac{J}{2\phi^M}\left(1 - \frac{J}{16\beta{\phi^M}^2}\right)\Sigma_M \right) \sinh \beta\phi^M\right\} \right.\\
			  &\quad\quad\quad\quad\quad\quad\quad\left.+ 2 M^2 e^{-\beta JM/2}\right]\\
where \(\Sigma_M = \sum_m (m+1/2)^2\).

If we take the limit of \(\beta \to \infty\), the hyperbolic functions can be replaced by exponentials. The terms with \(1/\beta\) in \(Z^{\prime\prime}\) drop out. All negative exponentials will also drop out. Moreover, out of all the positve exponentials, only the largest exponent will survive. The largest value \(\Phi\) of \(\phi^M\) occurs at \(M = M_\text{max} = K/2\). This maximum value is \(\Phi = J(K+1)/4\). We therefore have
\begin{equation}\begin{aligned}
	     Z(h \to 0) &= r^K_{K/2} 4Me^{\beta J/4}\frac{1}{2}e^{\beta\Phi}\\
	     Z^\prime(h \to 0) &= 0\\
	     Z^{\prime\prime}(h \to 0) &=\beta^2 r^K_{K/2}2 e^{\beta J/4}\frac{1}{2}e^{\beta \Phi}\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_\text{max}\\
\end{aligned}\end{equation}
The susceptibility at low temperatures becomes
\begin{equation}\begin{aligned}
	\chi(T \to 0) = \frac{2\beta\left(1 + \frac{J}{4\Phi}\right)^2\Sigma_M}{4M} = \frac{\beta \Sigma_\text{max}(K+2)^2}{K(K+1)^2}
\end{aligned}\end{equation}

\appendix
